A practical look at genetic algorithms

### 2015-11-28 evolutionaryComputation/practicals/report.tex
extended the report, now I want to make the uml, tried using tikz-uml
But it didn't work out very well, its to detailed, so now I'll switch to
emp, which seems easier in use, this is a safety commit

\begin{tikzpicture}
\begin{umlpackage}[x=0,y=0]{ec}
	\umlemptyclass[x=3]{Member}
\umlemptyclass{Population}
\umlemptyclass[x=6]{PairedPopulation}
%\umluniassoc[geometry=-|,arg1=x,mult1=1,pos1=1.9,arg2=y,mult2=*,pos2=0.2]{Population}{Member}
\end{umlpackage}
\end{tikzpicture}

@@

\subsection{Speed up attempts}
\subsubsection{Paralization}
Since were doing string comparisons I had the idea of ussing parlization to
speed up the algoritm by doing paralization. This can be done very easily
in scala with par collections (and the fact that imutibility is default).

@@

\input{result.tex}

>>>>

@@

\subsection{Speed up attempts}
I wanted my implementation to be fast, preferably faster than any other
implementation, now I think I didn't succeed in this because I used a
lot of slow mechanisms, such as functional combinators, and although
they don't increase the computational complexity, they do cerainly increase
the minimum required runtime, I'm quite sure that every combinator in sequance
is implemented as just another loop. However because I
run all expirments in paralel the total time may be faster.
\subsubsection{Paralization}
Since were doing string comparisons I had the idea of ussing parlization to
speed up the algoritm by doing paralization. This can be done very easily
in scala with par collections (and the fact that imutibility is default).

@@

Something to note is that my made up tournement elitism is actually in most
cases better, or at least equal to the truncate elitism. So when I saw
this I tried using my other initially used algorithm where I would completly
ignore the parents (kill the parents). However it appears this does not 
perform better.

I also added two point cross with mutation and 1 point cross to see how 
those fair, running the code now takes about 40 minutes in total with the
entire thing diveded over 8 threads (quad core + hyperthreading). The only
other improvement I could think of is running it on the GPU, but I think
the algortim is to complex for that.

Two point cross and single cross both seem to find results in deciptive 
random tournement elitism.

\newpage
\input{result.tex}
